The problem and promise of scale in multilayer animal social networks

### 2020-02-14 paper/manuscript.Rmd
update winpos fig cap

<!-- Figure: Window length -->
(ref:winlen) Varying scale in time window length. For each time window length (40 to 100 days in length increasing by 5 days in sequence), multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]`) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forest, forage, and open). A) Mean graph strength across individuals was relatively stable over increasing time window lengths, though there was more variation in strength between landcover types as window length increased. B) Mean layer relevance generally increased during the summer months but was relatively stable across time window lengths for each landcover layer. C) Similarity of landcover network layers between seasons (e.g. open summer compared to open winter) showed increasing similarity consistent across landcover layers with increasing window length. D) Mean connective redundancy across individuals varied dramatically depending on the length of the time window.

>>>>

<!-- Figure: Window length -->
(ref:winlen) Varying temporal scale in time window length. For each time window length (40 to 100 days in length increasing by 5 days in sequence), multilayer networks were constructed of caribou social associations (*Rangifer tarandus*, n = `r DT[, uniqueN(get(idcol))]`) on Fogo Island, Newfoundland in summer 2017 and winter 2018 across three habitat classes (forest, forage, and open). A) Mean graph strength across individuals was relatively stable over increasing time window lengths for winter layers, though there was more variation in strength between landcover types as window length increased. Summer layers an increase in strength for open and forage habitats. B) Mean layer relevance was stable for winter layers and increased for summer layers across habitat classes. C) Similarity of layers across habitat classes and between seasons (e.g. open summer compared to open winter) was relatively stable. D) Mean connective redundancy across individuals increased marginally with increasing window length.
